HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \parcite{lo2011structured}.
% SAVING SPACE:
% \XXX{Do we want to cut the following shorter?}
% However, 
% their focus on verb argument structures misses many semantic phenomena
% (such as inter-clause linkage and nominal argument structures), providing
% only
% a limited perspective on the semantic similarity between the translation and reference.
% Also, assigning semantic structure to an MT output, especially a poor one,
% is difficult and arguably ill-defined.

We propose the HUME metric,
a human evaluation measure that decomposes over the UCCA semantic units of the sentence.
UCCA\parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assesment scores which have been standardised for each crowdsourcing annotator. The regression is calculated using linear least squares.}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{TODO} has proposed a new method for collecting 
accuracy ratings. The idea is that collecting a large number of adequacy judgements along a 
scale of 0 to 100 allows us to apply statistical measures which make them reliable. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\cite{TODO} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romainian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We can see that HUME and Direct Assesment scores do correlate. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}. The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which shows that they two measures do correlate. This confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort, 
the results are more valuable because a HUME evaluation can tell you what parts
of the source sentence have been retained. Direct assesment scores require a crowd, which is sometimes not available or reliable, and it returns a single number which gives little insight into the quality of
the translated sentence.

@@

If only monolingual annotators are available, the HUME evaluation can be performed
with a reference sentence instead of with the source. 
% While HUME avoids this problem,
%imposing a structure only on the source does prevent any fine-grained semantic
%analysis of the translation.

>>>>

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \parcite{lo2011structured}.
% SAVING SPACE:
% \XXX{Do we want to cut the following shorter?}
% However, 
% their focus on verb argument structures misses many semantic phenomena
% (such as inter-clause linkage and nominal argument structures), providing
% only
% a limited perspective on the semantic similarity between the translation and reference.
% Also, assigning semantic structure to an MT output, especially a poor one,
% is difficult and arguably ill-defined.

We propose the HUME metric,
a human evaluation measure that decomposes over the UCCA semantic units of the sentence.
UCCA \parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assesment scores which have been standardised for each crowdsourcing annotator. The regression is calculated using linear least squares.}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{TODO} has proposed a new method for collecting 
accuracy ratings. The idea is that collecting a large number of adequacy judgements along a 
scale of 0 to 100 allows us to apply statistical measures which make them reliable. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\cite{TODO} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We can see that HUME and Direct Assesment scores do correlate. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}. The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which shows that they two measures do correlate. This confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort, 
the results are more valuable because a HUME evaluation can tell you what parts
of the source sentence have been retained. Direct assesment scores require a crowd, which is sometimes not available or reliable, and it returns a single number which gives little insight into the quality of
the translated sentence.

@@

If only monolingual annotators are available, the HUME evaluation could be performed
with a reference sentence instead of with the source. 
\bh{But this would be a different metric}
% While HUME avoids this problem,
%imposing a structure only on the source does prevent any fine-grained semantic
%analysis of the translation.
